### 2016-08-22 Engine.tex
完善node spliting

due to the effectiveness of the filter and the compactness of the AMT
whether there are patterns starting at that position

@@

Once the keys in a node share a common prefix, that prefix can be
removed from the keys and form a new single key node. This technique
can reduce a lot of redundant comparisons while searching a target key
in a node. For instance, consider searching a target key $a^5u$ in a
string array type node whose four keys share a common prefix $a^5$, as
shown in Fig . According to Algorithm \ref{alg:string array}, the
target key have to be compared sequentially with the four keys in the
node, which will totally takes $6 \times 4 = 24$ byte comparisons to
determine the inexistence of target key. However, if the common prefix
$a^5$ is split out and form another new node as shown in Fig , for the
same target, only 9 byte comparisons (5 comparisons for $node_1$ and
another 4 comparisons for $node_2$) are needed for
searching. Comparing with only one node, the two nodes can reduce 15
comparisons. Note that, since the prefix is either a character or a
string, the new node is either a Map 4 node or a String Array node.

>>>>

% due to the effectiveness of the filter and the compactness of the AMT
% whether there are patterns starting at that position

@@

In order to further improve the searching efficiency of tree nodes,
once the keys in a node share a common prefix, that prefix should best
be removed from the keys and form a new single key node. This method
can reduce a lot of redundant comparisons while searching a target key
in a node. For instance, consider searching a target key $a^5u$ in a
node of string array type, whose four keys share a common prefix $a^5$
, as shown in Fig . According to Algorithm \ref{alg:string array}, the
target key have to be compared sequentially with the four keys in the
node, which will totally takes $6 \times 4 = 24$ byte comparisons to
determine the inexistence of target key. However, if the common prefix
$a^5$ is removed out of the keys and form another new node as shown in
Fig , for the same target, only 9 byte comparisons are needed for
verifying (5 comparisons for $node_1$ and another 4 comparisons for
$node_2$). Note that, since the prefix is either a character or a
string, the type of the new node is either Map 4 or String
Array. Obviously, comparing with only one node, the two nodes version
can reduce 15 comparisons, which .
